Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-01 schemes.tex
Reviewing description of SRLNC

To achieve a desired average coding density in the coefficients, for each
of them, we utilize a set of Bernoulli random variables all with parameter $d$, i.e.
$\mathbb{B}_j \sim Bernoulli(d)\ ,\ \forall j \in [1,g]$. In this way, we
can represent a coded packet in \ac{SRLNC} as:
%One way to accomplish this is to add a Bernoulli random
%variable, $\text{B}(d)$, as in \ref{eq:sparse_coded_packet}:
\begin{align} \label{eq:sparse_coded_packet}
    %C_i  &= \bigoplus_{j=1}^{g} \text{B}(d)_{j} \, v_{ij} \otimes P_j ,\ \forall i \in [1,g] ,\
    C_i  &= \bigoplus_{j=1}^{g} \mathbb{B}_j v_{ij} \otimes P_j ,\ \forall i \in [1,g] ,\ \
    d \in
    \begin{cases}
        {(0,0.5]} & \text{for } q = 2 \\
        {(0,1]} & \text{for } q > 2
    \end{cases}
\end{align}
%
In \eqref{eq:sparse_coded_packet}, we have specified a dependency on the field size
for practical density values. In case of employing $GF(2)$, the maximum plausible
density is restricted up to 0.5 since higher values incur in more frequent \ac{l.d.}
coded packets \textbf{Include reference here}. Reducing $d$ enables the encoder to
decrease the average number of packets manipulated to make a coded packet. This
reduces the complexity of the encoder since it needs to mix less packets. Moreover,
it also simplifies the decoder processing given that less nonzero coding coefficients
required to be operated on during the Gaussian elimination stage.

The drawback of this scheme is that coded packets from the encoder become more \ac{l.d.}
on each other as the density is reduced. This incurs in transmission overhead
since more coded packets are required to be sent to overcome the reception of redundant
packets. Also, particularly with this method, generating a coded packet may imply
that it could not contain any data at all. For example, we might find the case
where $\left[\mathbb{B}_1, \ldots, \mathbb{B}_g \right] = \mathbf{0}$. In that case,
the encoder discards the coded packet and tries to generate a new one, though this is
unlikely to occur in general.

>>>>

To achieve a desired average coding density in the coefficients, for each
of them, we utilize a set of Bernoulli random variables all with parameter
$d$ as it success probability, i.e. $\mathbb{B}_j \sim Bernoulli(d)\ ,\ \forall
j \in [1,g]$. In this way, we can represent a coded packet in \ac{SRLNC} as:
%
\begin{align} \label{eq:sparse_coded_packet}
    C_i  &= \bigoplus_{j=1}^{g} \mathbb{B}_j v_{ij} \otimes P_j ,\ v_{ij}
    \neq 0\
    \forall i \in [1,\ldots) ,\ \
    d \in
    \begin{cases}
        {(0,0.5]} & \text{for } q = 2 \\
        {(0,1]} & \text{for } q > 2
    \end{cases}
\end{align}
%
In \eqref{eq:sparse_coded_packet}, we have the requirement for the coding
coefficient to not be zero, since we want to ensure a coding coefficient
is generate for any random trial where $\mathbb{B}_j = 1$. Therefore, in our
implementation of \ac{SRLNC} we exclude the zero element and then pick
uniformly distributed random elements from $GF(q)-\{ 0 \}$. Also, we have
specified a dependency on the field size for practical
density values. In case of employing $GF(2)$, the
maximum plausible density is restricted up to 0.5 since higher values incur
in more frequent \ac{l.d.} coded packets \textbf{Include reference here}.

Reducing $d$ enables the encoder to decrease the average number of packets
manipulated to make a coded one. This reduces the complexity of the encoder
since it needs to mix less packets. Moreover, it also simplifies the decoder
processing given that less nonzero coding coefficients are required to be
operated during the Gaussian elimination stage.

The drawback of this scheme is that coded packets from the encoder
become more \ac{l.d.} on each other as the density is reduced.
This leads to transmission overhead since another coded packet
is required to be sent for every reception of a redundant packet.
Also, particularly with this method, generating a coded packet may imply
that it could not contain any data at all. For example, we might find
the case where $\left[\mathbb{B}_1, \ldots, \mathbb{B}_g \right] =
\mathbf{0}$. In that case, the encoder discards the coded packet
and tries to generate a new one. This situation occurs more frequently
as the density is reduced.
